### 2024-03-26 doc/sections/mav-semantics.tex
[ agda tex ] more conceptual proof of reflection property

\begin{proposition}
  The \emph{cut-free MAV-frame} $\textsc{CFMav}$ is the partial order
  arising as the quotient of the preorder formed from the formulas of
  MAV and $P \leq Q$ if $P \longrightarrow^* Q$. Define
  $P \parallel Q = P \vParr Q$, $P \lhd Q = P \vSeq Q$,
  $P + Q = P \vWith Q$ and $I = \vUnit$. The required (in)equalities
  follow directly from the definition of $\longrightarrow^*$.
\end{proposition}

>>>>

\begin{proposition}\label{prop:cfmav-frame}
  The \emph{cut-free MAV-frame} $\textsc{CFMav}$ is the partial order
  arising as the quotient of the preorder formed from the formulas of
  MAV and $P \leq Q$ if $P \longrightarrow^* Q$. Define
  $P \parallel Q = P \vParr Q$, $P \lhd Q = P \vSeq Q$,
  $P + Q = P \vWith Q$ and $I = \vUnit$. The required (in)equalities
  follow directly from the definition of $\longrightarrow^*$.
\end{proposition}
